Abstractions for Multi-Sorted Substitutions

### 2024-03-15 paper/paper.tex
Update.

  We start with \ACode{\ACon{TKit}}s, which abstract over
  variable and term \emph{typing}, and then define a
  \ACode{\ACon{TTraversal}}, which provides
  substitution-preserves-typing for all \ACode{\ACon{TKit}}s.
  \LibCode\KTKit
  The fields of a \ACode{\ACon{TKit}} are completely analogous to
  those of a \ACode{\ACon{Kit}}, but talk about typing instead of terms.
  Building on the fields of a \ACode{\ACon{TKit}}, we define further operations:
  \begin{itemize}
  \item
    Using the variable/term typing, we can define a renaming/substitution typing:
    \LibCode\KMapTyping
    \ACode{ϕ \ADef{∶} Γ₁ \ADef{⇒ₖ} Γ₂} states that \ACode{ϕ} is a map that takes
    terms in \ACode{Γ₁} to terms in \ACode{Γ₂}.
  \item 
    Lifting a map preserves its typing:
    \LibCode\KLiftTyping
    % \LibCode\KLiftTypingProof
  \item 
    If a variable/term has a typing, then so does its singleton renaming/substitution:
    \LibCode\KSingleTyping
    % \LibCode\KSingleTypingProof
  \end{itemize}
  % To make it easier to explicitly pass typing kits,
  % we define the notation \ACode{ϕ \ADef{∶} Γ₁ \ADef{⇒[} TK \ADef{]} Γ₂}
  % to stand for \ACode{ϕ \ADef{∶} Γ₁ \ADef{⇒ₖ} Γ₂} of some
  % \ACode{\ACon{TKit}} \ACode{TK}.
  % \LibCode\KTypingNotation

  We then define a \ACode{\ACon{TTraversal}} analogously to
  \ACode{\ACon{Traversal}}, but instead of defining the application of
  % maps, it defines that the application of typed maps preserves term types:
  maps, it defines that the application of a typed map to a typed term yields a typed term:
  \LibCode\KTTraversal
  Given a term \ACode{e} with typing \ACode{⊢e} and
  a renaming/substitution \ACode{ϕ} with typing \ACode{⊢ϕ},
  the term \ACode{⊢e \AField{⊢⋯} ⊢ϕ} is a typing for \ACode{e \AField{⋯} ϕ}.
  The large amount of kit-parameters does not impose any restriction,
  as both our \ACode{\ACon{Kit}}s support the \ACode{\ACon{WkKit}}
  extension and can be composed arbitrarily. They only make the previously
  built machinery available to the proof of \ACode{\AField{\_⊢⋯\_}}.

  Given a \ACode{\ACon{TTraversal}}, we can easily instantiate the
  \ACode{\ACon{TKits}} for variables and terms:
  \LibCode\KTypingInstances

>>>>

  We start with \ACode{\ACon{TKit}}s, which abstract over
  variable and term \emph{typing}, and then define a
  \ACode{\ACon{TTraversal}}, which provides
  substitution-preserves-typing for all \ACode{\ACon{TKit}}s.
  \LibCode\KTKit
  The first field abstracts over variable and term typing.
  The other fields express typings for the fields of a \ACode{\ACon{Kit}}.
  Building on the fields of a \ACode{\ACon{TKit}}, we define map
  typing and type preservation for map lifting and the singleton map
  in the record module of \ACode{\ACon{TKit}}:
  \begin{itemize}
  \item
    Using the variable/term typing, we can define a renaming/substitution typing:
    \LibCode\KMapTyping
    \ACode{ϕ \ADef{∶} Γ₁ \ADef{⇒ₖ} Γ₂} states that \ACode{ϕ} is a map that takes
    terms from \ACode{Γ₁} to terms in \ACode{Γ₂}.
  \item 
    Lifting a map preserves its typing:
    \LibCode\KLiftTyping
    % \LibCode\KLiftTypingProof
  \item 
    If a variable/term has a typing, then so does its singleton renaming/substitution:
    \LibCode\KSingleTyping
    % \LibCode\KSingleTypingProof
  \end{itemize}
  % To make it easier to explicitly pass typing kits,
  % we define the notation \ACode{ϕ \ADef{∶} Γ₁ \ADef{⇒[} TK \ADef{]} Γ₂}
  % to stand for \ACode{ϕ \ADef{∶} Γ₁ \ADef{⇒ₖ} Γ₂} of some
  % \ACode{\ACon{TKit}} \ACode{TK}.
  % \LibCode\KTypingNotation

  We then define a \ACode{\ACon{TTraversal}} analogously to
  \ACode{\ACon{Traversal}}, but instead of defining the application of
  % maps, it defines that the application of typed maps preserves term types:
  maps, it defines that the application of a typed map to a typed term yields a typed term:
  \LibCode\KTTraversal
  Given a term \ACode{e} with typing \ACode{⊢e} and
  a renaming/substitution \ACode{ϕ} with typing \ACode{⊢ϕ},
  the term \ACode{⊢e \AField{⊢⋯} ⊢ϕ} is a typing for \ACode{e \AField{⋯} ϕ}.

  As before, we define the \ACode{\ACon{TKit}} instances in the record module
  of \ACode{\ACon{TTraversal}}:
  \LibCode\KTypingInstances

  The large amount of kit-parameters of \ACode{\AField{\_⊢⋯\_}} does
  not impose any restriction, as both our \ACode{\ACon{Kit}}s support
  the \ACode{\ACon{WkKit}} extension and can be composed
  arbitrarily. Agda's instance resolution allows us to easily
  instantiate a concrete substitution-preserves-typing lemma:
  \LibCode\KTPresS
